Behavior Driven Development in Haskell

### 2012-05-31 paper.tex
new abstract.

So, we need common syntax to describe examples and properties
independently in Haddock. Doctest should automatically verify
examples and test properties.

@@

@@

\begin{itemize}
\item
    For user documentation,
    Haddock does not have markups to describe evidence.
\item
    For code documentation,
    Hspec does not provide combinators to express expectations with
    BDD terminology.
\end{itemize}

>>>>

\begin{quote}
    \emph{kazu: I would like to add the following:}

So, we need common syntax to describe examples and properties
independently in Haddock. Doctest should automatically verify
examples and test properties.
\end{quote}

@@

\begin{quote}
    TBD: sol: @kazu, can you update this?
\end{quote}

@@

\begin{itemize}
\item
    The Haskell community does not have common syntax to describe
    evidence with Haddock markup syntax.
\item
    The Haskell community does not have a BDD tool for user documentation.
\item
    Hspec does not provide combinators to express expectations with
    BDD terminology.
\end{itemize}
